Capstone Movielens Report

### 2025-09-18 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Last update made on June 2025.

::: {.noteblock data-latex=""}
Unfortunately, for some reason, we do not see any improvement here yet.
:::

@@

::: {.noteblock data-latex=""}
As we can see, the current model still does not show much improvement after _regularization_, even though the data analysis we made in the [Movie Genres Effect] section showed strong evidence of a genre effect.
It looks like we need a better model to account for a genre effect more efficiently.

Or, maybe, we have implemented the current model not quite correctly (?)
:::

>>>>

::: {.noteblock data-latex=""}
Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
:::

Unfortunately, for some reason, we do not see any improvement here yet.

@@

::: {.noteblock data-latex=""}
Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
:::

As we can see, the current model still does not show much improvement after _regularization_, even though the data analysis we made in the [Movie Genres Effect] section showed strong evidence of a genre effect.
It looks like we need a better model to account for a genre effect more efficiently.

Or, maybe, we have implemented the current model not quite correctly (?)

### 2025-09-18 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Last update made on June 2025.

::: {.noteblock data-latex=""}
Now, we have a bit better result than one for the previous model.
:::

@@

>>>>

::: {.noteblock data-latex=""}
Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
:::

Now, we have a bit better result than one for the previous model.

@@

::: {.noteblock data-latex=""}
Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Common Helper Functions: Result RMSEs Table] section of the [Appendix] to this report.
:::

### 2025-09-18 reports/capstone-movielens.site/05.appendix.Rmd
Last update made on June 2025.

::: { #func.RMSEs.params .sidebar }
##### Parameters
\

::: { #func.RMSEs.params.RMSEs .sidebar }
  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;

@@

::: { #func.RMSEs.params. .sidebar }
  - ***:*** ;

@@

#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L) Function {#func.RMSEs.AddRow}
\

@@

::: { #func.RMSEs.params. .sidebar }
  - ***method:*** The _Method or Model_ being evaluated;

@@

::: { #func.RMSEs.params. .sidebar }
  - ***value:*** The _Root Mean Squared Error (RMSE)_ value;

@@

::: { #func.RMSEs.params. .sidebar }
  - ***comment:*** Detailed information about the record or any other comment (if needed);

@@

::: { #func.RMSEs.params. .sidebar }
  - ***before:*** One-based row index where to add the new rows, if NULL (default): after last row;

@@

>>>>

::: { #func.RMSEs..params .sidebar }
##### Parameters
\

::: { #func.RMSEs..params.RMSEs .sidebar }
  - ***RMSEs:*** _Resut (RMSEs) Table_ to modify;

@@

::: { #func.RMSEs..params. .sidebar }
  - ***:*** ;

@@

#### [RMSEs.AddRow](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L38) Function {#func.RMSEs.AddRow}
\

::: {.noteblock data-latex=""}
The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L38) script on _GitHub_.
:::

@@

::: { #func.RMSEs.AddRow.params.method .sidebar }
  - ***method:*** The _Method or Model_ being evaluated;

@@

::: { #func.RMSEs.AddRow.params.value .sidebar }
  - ***value:*** The _Root Mean Squared Error (RMSE)_ value;

@@

::: { #func.RMSEs.AddRow.params.comment .sidebar }
  - ***comment:*** Detailed information about the record or any other comment (if needed);

@@

::: { #func.RMSEs.AddRow.params.before .sidebar }
  - ***before:*** One-based row index where to add the new rows, if NULL (default): after last row;

@@

#### [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) Function {#func.RMSE_kable}
\

::: {.noteblock data-latex=""}
The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) script on _GitHub_.
:::

Prints the _Resut (RMSEs) Table_.

::: {.noteblock data-latex=""}
It is assumed that the table has the following three columns:

  1. *Method*;
  2. *RMSE*;
  3. *Comment*;

::: { #func.RMSE_kableusage .sidebar }
##### Usage
\

```{r eval=FALSE}
RMSE_kable <- function(RMSEs,
                       col1width = 15,
                       col2width = 5,
                       col3width = 30)
```
:::

::: { #func.RMSE_kable.params .sidebar }
##### Parameters
\

::: { #func.RMSE_kable.params.RMSEs .sidebar }
  - ***RMSEs:*** _Resut (RMSEs) Table_ to print;

::: { #func.RMSE_kable.params.col1width .sidebar }
  - ***col1width:*** Width of the first column;

::: { #func.RMSE_kable.params.col2width .sidebar }
  - ***col2width:*** Width of the second column;

::: { #func.RMSE_kable.params.col3width .sidebar }
  - ***col3width:*** Width of the third column;

::: { #func.RMSE_kablecode .sidebar }
##### Source Code
\

The soure code of the function is provided below:
```{r eval=FALSE}
RMSE_kable <- function(RMSEs,
                       col1width = 15,
                       col2width = 5,
                       col3width = 30){
  RMSEs |>
    kable(align='lcl', booktabs = T, padding = 5) |> 
    row_spec(0, bold = T) |>
    column_spec(column = 1, width = RSME.tibble.col_width(col1width)) |>
    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) |>
    column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
}
```
:::

#### [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L85) Function {#func.RMSE.Total_kable}
\

::: {.noteblock data-latex=""}
The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L85) script on _GitHub_.
:::

Prints the _Resut (RMSEs) Table_.

::: {.noteblock data-latex=""}
It is assumed that the table has the following four columns:

  1. *Method*;
  2. *RMSE*;
  3. *Diff*;
  4. *Comment*;

::: { #func.RMSE.Total_kableusage .sidebar }
##### Usage
\

```{r eval=FALSE}
RMSE.Total_kable <- function(RMSEs,
                       col1width = 15,
                       col2width = 7,
                       col3width = 5,
                       col4width = 25)
```
:::

::: { #func.RMSE.Total_kable.params .sidebar }
##### Parameters
\

::: { #func.RMSE.Total_kable.params.RMSEs .sidebar }
  - ***RMSEs:*** _Resut (RMSEs) Table_ to print;

::: { #func.RMSE.Total_kable.params. .sidebar }
  - ***col1width:*** Width of the first column;

::: { #func.RMSE.Total_kable.params. .sidebar }
  - ***col2width:*** Width of the second column;

::: { #func.RMSE.Total_kable.params. .sidebar }
  - ***col3width:*** Width of the third column;

::: { #func.RMSE.Total_kable.params. .sidebar }
  - ***col4width:*** Width of the fourth column;

::: { #func.RMSE.Total_kablecode .sidebar }
##### Source Code
\

The soure code of the function is provided below:
```{r eval=FALSE}
RMSE.Total_kable <- function(RMSEs,
                       col1width = 15,
                       col2width = 7,
                       col3width = 5, 
                       col4width = 25){
  RMSEs |> 
    RMSE_kable(col1width,
               col2width,
               col3width) |>
    column_spec(column = 4, 
                width = RSME.tibble.col_width(col4width)) 
}

::: {.noteblock data-latex=""}
Under the hood, the function calls internally the [RMSE_kable](#func.RMSE_kable) function described above.
:::
:::
